High-level cognition is supported by at least second order dynamic correlations in neural activity patterns

### 2019-09-03 paper/main.tex
backing up progress on results section

>>>>

Both sets of temporal decoding analyses yielded qualitatively similar
results for the auditory (non-rest) conditions of the experiment.  The
highest decoding accuracy for participants who listened to the intact
(unscrambled) story was achieved using high-order dynamic correlations (PCA:
second-order; eigenvector-centrality: fourth-order).  Scambled
versions of the story were best decoded by lower-order correlations
(PCA/paragraph: first-order; PCA/word: order zero; eigenvector
centrality/paragraph: order zero; eigenvector centrality/word: order
zero).  The two sets of analyses yielded different results on resting
state data (which we note could be decoded only very slightly above
chance).  The PCA-based approach achieved the highest resting state
decoding accuracy using order zero features (non-correlational
activation-based), whereas the eigenvector centrality-based approach
achieved the highest resting state decoding accuracy using
second-order correlations.
